### 2016-09-01 ReviewComments/meta.tex
Another draft
Proof read before submiting

\emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}

\response{In addition to the points in Response 2, another novelty of our work lies in the 
techniques. 
Although the idea of star partition and apriori enumeration are well-known, 
linking them together to solve the problem in trajectory domain has not been attempted before.
Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
anti-monotonicity) which have not been previously proposed.
}

\emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
on the motivation.}

\response {Similar responses with Response 3. }

\emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce. Spark has capabilities beyond MapReduce such as window functions. Please provide an implementation that uses the relevant features of Spark, or a convincing discussion of how these features can be useful and why they were not used.}

\response{Similar responses with Response 1 and 5. }

\emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew. Also provide details about how star partitioning and a priori pruning contribute to performance. Please provide references to these two methods.}

\response { 
Similar responses with Response 6, 7 and 9.
}

>>>>

\textbf{M.1} \emph{Novelty: The GCMP generalization is not particularly novel. Please elaborate on the novelty of the work.}

\textbf{Response:} In addition to the points in the response of comments 2.1, another novelty of our work lies in the 
techniques. 
Although the idea of star partition and apriori enumeration are well-known, 
linking them together to solve the problem in trajectory domain has not been attempted before.
Besides, we input heavy details on these algorithms (e.g., theoretical bounds of partition and
anti-monotonicity) which have not been previously proposed.

\textbf{M.2} \emph{Parameter setting: Are we really interested in all sets of movements beyond a cardinality of size M? Please elaborate
on the motivation.}

\textbf{Response:} Addressed in the response for comments 2.2.

\textbf{M.3} \emph{Spark implementation: the paper references Spark as the implementation platform but the algorithm is limited to MapReduce. Spark has capabilities beyond MapReduce such as window functions. Please provide an implementation that uses the relevant features of Spark, or a convincing discussion of how these features can be useful and why they were not used.}

\textbf{Response:} Addressed in the response for comments 1.1 and 3.1.

\textbf{M.4} \emph{More details in the performance evaluation: Please provide more details about data partitioning and the effect of skew. Also provide details about how star partitioning and a priori pruning contribute to performance. Please provide references to these two methods.}

\textbf{Response:} Addressed in the response for comments 3.2, 3.3, 3.4 and 3.6.

### 2016-09-01 ReviewComments/review2.tex
Another draft
Proof read before submiting

\textbf{Response:}
We admit that the gap parameter is also used in
mining Gap-restricted Sequential Patterns (GSP). 
However, the novelty of this paper lies
on the one-stop solution of mining co-movement patterns.
In modeling, we provide the generalize co-movement pattern to
alleviate the troubles
is not merely on introducing the gap-constraint.
Instead, we provide a one-stop solution for mining co-movement patterns. With
our

However, the novelty
of this paper is not merely on introducing the gap-constraint to the generalized
co-movement pattern. 
Instead, we provide a one-stop solution (both in modeling and in technical)
for mining various co-movement patterns with flexible constraints.

This solution not only alleviate the cumbersome for designing each
individual patterns, but also

 With
these constraints, users are able to define a more accurate pattern
which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).

Besides, the essence of GSP and GCMP are different. The goal of GSP 
is to find the sequences which conform to the gap constraint and occur frequently.
When counting the occurrence of a sequence in GSP, the object
which a sequence belongs to does not matter. Therefore, 
in a GSP result, the involved objects may be neither
 distinct nor close.
In contrast, GCMP imposes requirements on both the spatial closeness 
of objects and the number of distinct objects.
Due to the unawareness of objects, techniques that are used in GSP 
cannot be directly applied on GCMP. We summarize this difference
in Section 2.5.

\emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
we really interested in all sets of movements beyond a cardinality of size $M$? 
Take the Taxi dataset as an example. Let say that there are lots of taxis going
from the airport to downtown. Let say that there are 1000 such taxis. For a
given $M$, are we interested in ${1000 \choose M}$ answers? 
So this speaks to the problem of picking $M$. If $M$ is 500, what is ${1000 \choose M}$? In fact, even if the
system gives the single answer of ${1000\choose 1000}$,
I am not sure I am
interested in this pattern as I already know that there are many taxis going from
the airport to downtown. What I think I am really interested in are GCMP that
are ``anomalous'', which is much harder to define.}

\response{We appreciate the reviewer's concerns on the 

@@

}

\emph{Regarding the second weak points, one line of related work is the superimposition
of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}

\response{We understand that spatiotemporal mining with domain-constraints
looks similar to GCMP.
However, those techniques often heavily utilize the domain knowledge (such as
directions in road networks) which are nontrivial to be generalized.
Differently, since our GCMP model and technical solutions
do not leverage the domain knowledge, we can support
pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
passenger flows in a city. We also add the discussion in Section 2.3.
}

>>>>

\textbf{Response:} We admit that the gap parameter
is also used in mining Gap-restricted Sequential Patterns (GSP). 
However, our work is the first to introduce the gap concept 
in co-movement mining to resolve the
loose-connection anomaly (as shown in Figure 2).  
Moreover, we also provide
a unified model to capture existing pattern models which 
is also not proposed before.
%
%The novelty of our modeling
%is bi-folded. First, we unify existing co-movement patterns in
%a GCMP model. Second, we use the gap-constraint to avoid
%the loose-connection anomaly (as shown in Figure 2) which 
%is suffered by existing patterns.

%
%We admit that the gap parameter is also used in
%mining Gap-restricted Sequential Patterns (GSP). 
%However, the novelty of this paper lies
%on the one-stop solution of mining co-movement patterns.
%In modeling, we provide the generalize co-movement pattern to
%alleviate the troubles
%is not merely on introducing the gap-constraint.
%Instead, we provide a one-stop solution for mining co-movement patterns. With
%our 
%
%However, the novelty
%of this paper is not merely on introducing the gap-constraint to the generalized
%co-movement pattern. 
%Instead, we provide a one-stop solution (both in modeling and in technical)
%for mining various co-movement patterns with flexible constraints.
%
%This solution not only alleviate the cumbersome for designing each
%individual patterns, but also 
%
% With
%these constraints, users are able to define a more accurate pattern
%which are free from the anomalies (e.g., loss-connection anomaly in Figure 2).

Besides, GSP and GCMP are designed with different goals. Thus it is infeasible
to model GCMP using GSP. 
In particular, the goal of GSP 
is to find the frequently occurred subsequences which conform to the gap constraint.
This definition ignores the relationships among the involved objects. 
As a consequence, the mined GSP results cannot guarantee the spatial closeness of the involved
objects, which contradicts with \emph{closeness} requirement of GCMP (Section 3 Definition 2). 
For example, in the sample trajectory database in Figure 1, 
the most frequent temporal sequence for GSP is
$(1,2,3,4,5,6)$ because it appears in all trajectories. 
However, the involved objects $\{o_1,o_2,o_3,o_4,o_5,o_6\}$ are NOT all
spatially close at any of the timestamps thus these objects do not form a proper GCMP.
We summarize this difference in Section 2.5.

%
%
%When counting the occurrence of a subsequence, the object
%which the subsequence belongs to does not matter. This allows an object
%to contribute multiple times for a subsequence's occurrence (e.g., in ``$o_1:ABCDABC$", $o_1$
%contributes twice for the subsequence $ABC$)
%
%As a result, GSP may double count an object if the object's sequence 
%has two identical subsequence.
%
%the involved objects may be neither
% distinct nor close.
%In contrast, GCMP imposes requirements on both the spatial closeness 
%of objects and the number of distinct objects.
%Due to the unawareness of objects, techniques that are used in GSP 
%cannot be directly applied on GCMP. We summarize this difference
%in Section 2.5.

\textbf{2.2} \emph{In fact, I have doubts about formulating the GCMP patterns as proposed. Are
we really interested in all sets of movements beyond a cardinality of size $M$? 
Take the Taxi dataset as an example. Let say that there are lots of taxis going
from the airport to downtown. Let say that there are 1000 such taxis. For a
given $M$, are we interested in ${1000 \choose M}$ answers? 
So this speaks to the problem of picking $M$. If $M$ is 500, what is ${1000 \choose M}$? In fact, even if the
system gives the single answer of ${1000\choose 1000}$,
I am not sure I am
interested in this pattern as I already know that there are many taxis going from
the airport to downtown. What I think I am really interested in are GCMP that
are ``anomalous'', which is much harder to define.}

\textbf{Response:} We appreciate the reviewer's concerns on the 

@@

\textbf{2.3} \emph{Regarding the second weak points, one line of related work is the superimposition
of constraints on spatiotemporal mining. An example is a road network. In other words, given a road network, the network imposes constraints on GCMP.}

\textbf{Response:} We understand that spatiotemporal mining with 
domain-specific constraints may look similar to GCMP.
However, we are unaware of existing works on the same GCMP model
 with domain-specific constraints.

Generally, patterns defined with domain-specific constraints are hard to be generalized.
This is because constraints available in one domain (e.g., road direction in road networks)
are often not available in other domains (e.g., no road directions available for visitor movements in a shopping mall). Nevertheless,
when deploying on a specific domain, our GCMP solutions are amendable to
incorporate more domain-specific constraints (i.e., rewrite the $\mathtt{sim}$ operation in Algorithm 3). 
We summarize the discussion in Section 2.3.

%often rely on the specific knowledge in that domain (e.g.,
%directions in road networks and maximum speed of traffic), which
%are hard to be generalized. In contrast, GCMP's constraints
%are on spatial (i.e., closeness) and temporal (e.g., max gap and min duration), 
%which can be generalized for all trajectories. For example,
%mining techniques on road networks fails to find patterns
%in  
%
%However, existing techniques on spatiotemporal mining with domain-specific  
%
%
%those techniques often heavily utilize the domain knowledge (such as
%directions in road networks) which are nontrivial to be generalized.
%Differently, since our GCMP model and technical solutions
%do not leverage the domain knowledge, we can support
%pattern discovery in broader scenarios such as user check-in histories in social networks, visitor movements in a building and 
%passenger flows in a city.

### 2016-09-01 ReviewComments/review3.tex
Another draft
Proof read before submiting

\section{Responses to Reviewer 3}
\emph{Though the implementation references Spark as the implementation
platform (as it also reflects in github repo provided), the algorithm design is
mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
Spark. This may have a negative impact on the baseline implementation.
Particularly, recent releases of Spark have introduced window functions that can
be applied directly in the sliding window scenario here. Certainly, the algorithm
has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
been noted that this is a very efficient way to execute window functions in
Spark}

\response{
We thank the reviewer for suggesting a better way of implementing 
the baseline algorithm (i.e., TRPM). However, this could
hardly be done after our investigations. The major reason is
that current version of Spark SQL (i.e., 1.6.2 released in June)
does not support the User Defined Aggregate Function (UDAF) on window
function~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
our Line sweep algorithm (Algorithm 1) using Spark SQL 
primitive aggregates (e.g., sum, avg, rank and nth-tile)
is beyond our abilities.

Further, we believe the performance boost on TRPM from Spark SQL
is very limited. The reason is that our 
Line Sweeping Mining algorithm (Algorithm 1) is not a 
properly reducible function. That is, the result of a 
smaller window could not be used to compute the result of a larger
window. In such a case, Spark SQL has to process each
window independently in parallel, which is equivalent to our TRPM implementation.
%We agree that leveraging more advanced Spark features
%could further improve the performance of our solutions. 
%We do not heavily leverage these features because 
%we wish to focus on designing parallel GCMP mining algorithms.
%%to provide a general parallel framework which does not tie to Spark.
%Nevertheless, we are in progress in developing
%a better open-sourced version with Spark-tailored optimization. 
%In the revision, we try to add a DataFrame based TRPM solution 
%which aims to leverage the window functions from Spark-SQL.
%However, to the best of our efforts, we could not achieve this goal in a short time. 
%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
%is nontrivial. Nonetheless, we expect less performance
%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
%properly reducible, where Spark system would fail to leverage the partial aggregates
%across multiple windows. As a result, it would be equivalent to our current TRPM
%solution where windows are processed independently in parallel.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable. 
}

\emph{In particular, it would be great to provide the
difference in the number of partitions/splits, the amount of processing and
memory usage (i.e., vcore and memory seconds) between TRPM and SPARE}

\response{We add Table 7 to include vcore-seconds 
and RDD memory usage for both TRPM and SPARE. We also add a clear description on partitions in Section 6.
}

\emph{A plot that breaks down the performance gain by each method would
be greatly appreciated by the readers.}

\response{We complement Figure 8 with the breakdown cost of TRPM. This
comparison showcases the benefits of both Star Partition (in mapshufle phase)
and Apriori Enumeration (in reduce phase) of SPARE.
}

\emph{Some choices of words may need to be reconsidered: for example, "a bunch
of" might not be appropriate in a technical paper.}

\response{We thank the reviewer for the correction. We have changed many unprofessional terms.
}

\emph{References to star partitioning and apriori pruning are missing. Though these
are well known, they need to clearly cited. At least the following reference is
missing:}

\response{We add the corresponding references in Section 5.1 and Section 5.2.}

\emph{In "In contrast, when utilizing the multicore
environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was "multicore"
referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}

\response{ We use all cores in a single node to conduct the experiments. We revise the description in Section 6.2.3.
}

\emph{The computation of "eta" was slightly different than that in the paper}

\response{
We have updated the GitHub repository to rectify the typo in the equation.}

>>>>

\section{Responses to Reviewer 3}
\textbf{3.1:} \emph{Though the implementation references Spark as the implementation
platform (as it also reflects in github repo provided), the algorithm design is
mostly limited to MapReduce, aka only Hadoop, which is a very small subset of
Spark. This may have a negative impact on the baseline implementation.
Particularly, recent releases of Spark have introduced window functions that can
be applied directly in the sliding window scenario here. Certainly, the algorithm
has to be redesigned to use DataFrame (and/or Spark SQL) interface, it has
been noted that this is a very efficient way to execute window functions in
Spark.}

\textbf{Response:}
We thank the reviewer for suggesting a better way of implementing 
the baseline algorithm (i.e., TRPM). By utilizing window functions,
TRPM could be rewritten as in the following pseudo-code:
\begin{equation*}
\begin{aligned}
 \mathtt{WindowSpec}\ ws := \mathtt{Window}&.\mathtt{orderBy}('time') \\
 				&.\mathtt{rangeBetween}(0, \eta); \\
 \mathtt{Pattern}\ pt :=  LineSweep&('clusters').\mathtt{over}(ws); 
\end{aligned}
\end{equation*}

However, the algorithm is challenging
to be implemented after our investigations. The major reason is
that, in current version of Spark-SQL~\footnote{Both the stable Spark 1.5.2 and the newly released Spark 1.6.2}, 
User Defined Aggregate Function (UDAF) on window operator is not supported~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. 
Without UDAF, we cannot attach the $\mathtt{over}$ keyword to
the Line Sweep algorithm. A workaround is to implement the Line Sweep using only Spark-SQL primitive aggregate 
functions (e.g., sum, avg, rank and nth-tile). But it
is beyond our abilities.
%
%we cannot integrate the Line Sweep algorithm with window functions 
%(i.e., with the $\mathtt{over}$ keyword). On the other hand,
%implementing the Line Sweep algorithm (Algorithm 1) using Spark-SQL 
%primitive aggregates (e.g., sum, avg, rank and nth-tile)
%is beyond our abilities.

On the other hand, we believe the performance boost on TRPM from Spark-SQL
would be very limited. The reason is that our 
Line Sweep algorithm (Algorithm 1) is not a 
distributive function. 
That is the result over an input cannot be constructed from
the result over a subset of the input. This indicates 
that no partial results can be shared among all windows.
In such a case, Spark-SQL has to process each
window independently in parallel, which is equivalent to our TRPM implementation.
%We agree that leveraging more advanced Spark features
%could further improve the performance of our solutions. 
%We do not heavily leverage these features because 
%we wish to focus on designing parallel GCMP mining algorithms.
%%to provide a general parallel framework which does not tie to Spark.
%Nevertheless, we are in progress in developing
%a better open-sourced version with Spark-tailored optimization. 
%In the revision, we try to add a DataFrame based TRPM solution 
%which aims to leverage the window functions from Spark-SQL.
%However, to the best of our efforts, we could not achieve this goal in a short time. 
%The major challenge is that current Spark do not support User Defined Aggregate Function (UDAF)
%in window functions~\footnote{JIRA Spakr-8641: Native Spark Window Functions \url{https://issues.apache.org/jira/browse/SPARK-8641}}. Without UDAF, implementing
%our Line sweep algorithm (Algorithm 1) using Spark primitives (e.g., sum, avg, rank and nth-tile)
%is nontrivial. Nonetheless, we expect less performance
%boost from TRPM even with the UDAF support. This is because the Line sweep algorithm is not
%properly reducible, where Spark system would fail to leverage the partial aggregates
%across multiple windows. As a result, it would be equivalent to our current TRPM
%solution where windows are processed independently in parallel.
%TRPM although can be modeled using window functions over data frame, the aggregates
%it uses (i.e., the Line Sweeping method in Algorithm 1) cannot be simply represented
%by Spark primitives (e.g., sum, avg, rank, nth-tile). We then resort to
%the Spark User Defined Aggregate Function (UDAF). However, in Spark 1.5.2, the UDAF
%does not support window function syntax. Even in the latest Spark 1.6.0 (released 
%last month), UDAF does not fit with window function. We confirm these information
%with Spark development team~\footnote{In Spark JIRA tickets, fully supporting UDAF is still under development}.
%
%Nevertheless, since our Algorithm 1 is not reducible, even with UDAF, TRPM could
%not boost too much 
%
%we expect
%even with UDAF support TRPM would not boost too much.  Spark system is 
%%hard to leverage the partial aggregates acrocess
%
%we can analytically expect even using UDAF, TRPM would
%not boost too much. This is because our Algorithm 1 is not reducible. That
%is we cannot merge or share partial aggregates across different windows. In summary,
%We wish to convince the reviewer that current TRPM implementation is reasonable.

\textbf{3.2:} \emph{Most implementations
on Hadoop and Spark are very sensitive to data partitions, i.e. prone to data
skewing issues. It seems that the (starpartition)
implementation does not take
this into account, and only use the default partitioning. It would be very helpful
to have a discussion on this topic.}

\textbf{Response:}  We study the skewness by examining the load balance of each algorithm.
We revise Section 6.2.2 by comparing SPARE with different data partition strategies.
In particular, we compare SPARE which adopts a best-fit strategy (Section 5.3) and SPARE-RD
which adopts the default random partition strategy.
We present the summary of the execution time for each method on the longest job, the shortest job and standard
deviation of all jobs in Table 9. As the table shows, SPARE has a better load balance (low deviation)
than SPARE-RD which indicates the effectiveness of the best-fit strategy. 
%Further, TRPM generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition. Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.

%We revise Section 6.2.2 by comparing TRPM, SPARE with random 
%task allocation and SPARE with best-fit task allocation (Section 5.3). We present
%the summary of the execution time for each method on longest job, shortest job and standard
%deviation of all jobs in Table 9. As the table show, SPARE has a better load balance (low deviation)
%than SPARE-RD which indicates the effectiveness of the best-fit strategy. Further, TRPM
%generally keeps a low deviation. This is because that TRPM always adopts the equal-size (i.e. $\eta$) partition.
%Nevertheless, both the longest and shortest jobs in TRPM are higher than SPARE based solutions.

\textbf{3.3:} \emph{In particular, it would be great to provide the
difference in the number of partitions/splits, the amount of processing and
memory usage (i.e., vcore and memory seconds) between TRPM and SPARE}

\textbf{Response:} In our implementation, we take a fixed 486 partitions (Section 6)
for each RDD. The partition number is determined according to
the parallel tuning guide by Cloudera~\footnote{Spark Performance Tuning \url{http://blog.cloudera.com/blog/2015/03/how-to-tune-your-apache-spark-jobs-part-1/}}: there are  $3\times 54=162$ cores and each core is able to processes 3 partitions~\footnote{This number may differ for other CPU models, and can be determined empirically.}
by multithreading.

Next, we add Table 7 (Section 6.1) to compare
the resource usage (e.g., Vcore-seconds, Memory and Running Time) between SPARE and TRPM.
The table tells that both SPARE and TRPM are resource efficient.
In particular, the RDDs for both SPARE and TRPM only take less than 20\% of 
the available memory. This infers the potential of SPARE and TRPM in handling 
even larger trajectories with our current cluster resources.

\textbf{3.4:} \emph{A plot that breaks down the performance gain by each method would
be greatly appreciated by the readers.}

\textbf{Response:} We include the analysis of
the breakdown cost of SPARE by taking TRPM as
a reference in Figure 8. 
SPARE and TRPM algorithms are of the similar structure: partitioning (Star partition v.s. $\eta$-replicate
partition) is in the map-shuffle phase, and  mining (Apriori Enumeration v.s. Line Sweep) 
is in the reduce phase. In our experiment, we treat the execution time
for each phase as the cost of the corresponding methods.

As shown in Figure 8,
both star partition and apriori enumeration contribute to 
the final performance gain of SPARE. In particular, in the Map-Shuffle phase,
SPARE saves 56\%-73\% in time as compared to TRPM. This indicates that 
less data are transformed and shuffled in the Star partition.
In the Reduce phase, SPARE saves 46\%-81\% time as compared to TRPM. This confirms 
the efficiency of our Apriori enumerator.

% with various optimization (e.g., sequence simplification, anti-monotonicity and forward closure checking).

\textbf{3.5} \emph{Some choices of words may need to be reconsidered: for example, ``a bunch
of" might not be appropriate in a technical paper.}

\textbf{Response:} We have changed these unprofessional terms.

\textbf{3.6} \emph{References to star partitioning and apriori pruning are missing. Though these
are well known, they need to  be clearly cited.}

\textbf{Response:} We add the corresponding references in Section 5.1 and Section 5.2 when we
describing our algorithms.

\textbf{3.7} \emph{In ``In contrast, when utilizing the multicore
environment, SPAREP achieves 7 times speedup and SPARES achieves 10 times speedup.", was ``multicore"
referring to the use of all 16 cores in one of your node? The specification of the machine was not clear.}

\textbf{Response:} We use all cores in the single node (i.e., 4 executors each with 3 cores) to conduct the experiment. We revise the description in Section 6.2.3.

\textbf{3.8} \emph{The computation of "eta" was slightly different than that in the paper}

\textbf{Response:} We have updated the GitHub repository to rectify the typo in the equation.
